---
title: "Laying Asynchrony"
author: "Ivan Bizberg"
date: "17/6/2021"
output: 
  html_document:
    number_sections: true
    theme: journal
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: inline
---

```{r global-options, include=FALSE}
knitr::opts_chunk$set(fig.align = "center", fig.height = 10, fig.width = 15)
```


Libraries
```{r message=FALSE, warning=TRUE}
library(tidyverse)
library(magrittr)
library(lubridate)
library(ggthemes)
library(dtplyr)
library(data.table)

library(effects)
library(kableExtra)
library(formattable)
library(gridExtra)
library(grid)

library(performance)
library(DHARMa)
library(widyr)

library(climwin)
library(lme4)
library(glmmTMB)
library(ordinal)
library(VGAM)


path = "Conducta"
setwd("C:/Users/Conducta/Dropbox/PHD/Git/Hatching_Asynchrony/Laying_Asynchrony_F")
getwd()
```


# Import-Edit raw bio data
```{r message=FALSE, warning=TRUE}
Biodata <- read.csv(str_glue("C:/Users/{path}/Dropbox/PHD/DATA/ALLWORK2021.csv"),sep =",",
                    header = T, na.strings=c("","NA")) %>% mutate(across(c(ANILLOHEMB, ANILLOMACH), ~toupper(.))) %>% 
  mutate(SEMANIPULO = tolower(SEMANIPULO)) %>% 
  mutate(CAMBIO_REVISION = case_when(
    WORKYEAR == 1991 ~ "20-abr-1991",
    WORKYEAR == 1994 ~ "26-may-1994",
    WORKYEAR == 1995 ~ "8-jun-1995",
    WORKYEAR == 1996 ~ "21-abr-1996",
    WORKYEAR == 1997 ~ "24-may-1997",
    WORKYEAR == 1998 ~ "7-abr-1998",
    WORKYEAR == 1999 ~ "22-abr-1999",
    WORKYEAR == 2000 ~ "19-mar-2000",
    WORKYEAR == 2001 ~ "13-may-2001",
    WORKYEAR == 2002 ~ "12-mar-2002",
    WORKYEAR == 2004 ~ "17-abr-2004",
    WORKYEAR == 2005 ~ "29-may-2005",
    WORKYEAR == 2006 ~ "17-mar-2006",
    WORKYEAR == 2007 ~ "4-abr-2007",
    WORKYEAR == 2008 ~ "7-mar-2008",
    WORKYEAR == 2009 ~ "29-mar-2009",
    WORKYEAR == 2011 ~ "29-mar-2011",
    WORKYEAR == 2012 ~ "22-mar-2012",
    WORKYEAR == 2013 ~ "9-abr-2013",
    WORKYEAR == 2014 ~ "4-jun-2014",
    WORKYEAR == 2018 ~ "9-jun-2018",
    WORKYEAR == 2021 ~ "27-mar-2021"
  )) %>% mutate(CAMBIO_REVISION = dmy(CAMBIO_REVISION))

Biodata %>% select(CAMBIO_REVISION) %>% drop_na() %>% mutate(CAMBIO_REVISION = dmy(CAMBIO_REVISION)) %>% count(CAMBIO_REVISION)


Bioedit <- Biodata %>% 
  mutate(across(c(PUESTA1, PUESTA2, PUESTA3), mdy)) %>% # By using PUESTA and not ESTPUESTA i make sure to know the exact number of eggs and laying date
  mutate(Hatching_async = as.numeric(PUESTA2 - PUESTA1)) %>% 
  drop_na(Hatching_async) %>% 
  filter(Hatching_async >= 0 & Hatching_async <= 20) %>% 
  mutate(HA = cut(Hatching_async, c(-Inf, 2, 5, 8, Inf), labels = c(0, 1, 2, 3))) %>% 
  mutate(HA = as.numeric(as.character(HA))) %>% 
  filter(SEMANIPULO == "f") %>% 
  rename(Clutch = PUESTA) %>% 
  filter(!Clutch > 2) %>% # parasite or error
  group_by(NIDO) %>% 
  mutate(DATEmin = min(c(PUESTA1, PUESTA2), na.rm = T)) %>% 
  mutate(DATEmax = max(c(PUESTA1, PUESTA2), na.rm = T)) %>% 
  filter((Clutch == 2 & CAMBIO_REVISION > PUESTA2) | is.na(CAMBIO_REVISION)) %>%  # Remove nest where revision occures every 6 days
  as.data.frame()

BioMini <- Bioedit %>% select(WORKYEAR, NIDO, DATEmax, HA, PROPORTIONALRANK, AGEHEMB, ANILLOHEMB) %>% filter(!ANILLOHEMB == "SA")


Bioedit %>% count(HA)
BioMini %>% glimpse()
BioMini %>% drop_na() %>% count()
write_csv(Bioedit, "BioWinHA.csv")
```
Same results when filtering females that have more than 1 obs

# Import raw climatic data
```{r}
ClimData = read.csv(str_glue("C:/Users/{path}/Dropbox/PHD/DATA/Weather.csv"), sep = ",", header = T,stringsAsFactors = F) %>% 
  rename(Date = time, SST = sst, Area_Rain = rain) %>% mutate(Date = ymd(Date)) %>% 
  select(Date, SST, Area_Rain) 


plot(ClimData$SST)
plot(ClimData$Area_Rain)
```

# Check random effects
```{r}
Bio <- BioMini %>%  # This is for chlorophyll a
  mutate(across(c(everything(), -HA, -PROPORTIONALRANK, -AGEHEMB), as.character)) %>% 
  drop_na() %>% 
  mutate(across(c(WORKYEAR, ANILLOHEMB, NIDO), as.factor)) %>% 
  mutate(across(c(DATEmax), ymd)) %>% 
  glimpse()

baseline = lm(HA ~ PROPORTIONALRANK + AGEHEMB,
                REML = FALSE,
                data = Bio)
baselineclmm = clmm(factor(HA) ~ 1 + (1|WORKYEAR),
                REML = FALSE,
                data = Bio)
baselineglmer = glmer(HA ~ PROPORTIONALRANK + AGEHEMB + (1|WORKYEAR),
                family = poisson,
                data = Bio)
baseline_year = lmer(HA ~ PROPORTIONALRANK + AGEHEMB + (1|WORKYEAR),
                REML = FALSE,
                data = Bio)
baseline_age = lmer(HA ~ PROPORTIONALRANK + AGEHEMB + (1|ANILLOHEMB),
                REML = FALSE,
                data = Bio)
baselineglmer = glm(HA ~ PROPORTIONALRANK + AGEHEMB,
                family = poisson,
                data = Bio)
baseline_yearglmer = glmer(HA ~ PROPORTIONALRANK + AGEHEMB + (1|WORKYEAR),
                          family = poisson,
                          data = Bio)
baseline_ageglmer = glmer(HA ~ PROPORTIONALRANK + AGEHEMB + (1|ANILLOHEMB),
                         family = poisson,
                         data = Bio)

bbmle::AICtab(baselineglmer,baseline_yearglmer,baseline_ageglmer)
bbmle::AICtab(baseline,baseline_year,baseline_age)
bbmle::AICtab(baseline,baselineclmm, baselineglmer)
# Singular fit with both anillohemb and year as random effect only one one

# And femalle age does not improve the model
```



# Data Bio 1989
```{r}
# Biological data
Bio <- BioMini %>% filter(WORKYEAR >= "1989") %>% # This is for SST
  mutate(across(c(everything(), -HA, -PROPORTIONALRANK, -AGEHEMB), as.character)) %>% 
  drop_na() %>% 
  mutate(across(c(WORKYEAR, ANILLOHEMB, NIDO), as.factor)) %>% 
  mutate(across(c(DATEmax), ymd)) %>% 
  glimpse()
```

# Finding window for SST
```{r}
# Climatic data
Clim = ClimData %>% select(Date , SST) %>%
  na.omit()
```
### Climwin
```{r message=TRUE, results=TRUE, cache=TRUE}
ClimWin = slidingwin(xvar = list(ClimVar = Clim$SST), # Climatic variable
                     cdate = Clim$Date,
                     bdate = Bio$DATEmax,
                     baseline = glm(HA ~ PROPORTIONALRANK + AGEHEMB,
                                      family = poisson, 
                                      #nAGQ=0,
                                      data = Bio),
                     cinterval = "week",
                     range = c(10, 0), # max window used is 10   
                     type = "relative",
                     stat = c("min", "max", "mean"), 
                     func = c("lin", "quad"), # Best model with log and inv but hard to interpred and convergence problems with sum
                     cmissing = "method1")
```
No convergence problem with min quad
```{r}
Comb = (ClimWin$combos) %>% add_rownames() %>% arrange((DeltaAICc)); Comb
```
```{r}
n = Comb %>% .[[1,1]] %>% as.numeric()
tidy_stat = Comb %>% .[[1, 5]] %>% as.character()
tidy_func = Comb %>% .[[1, 6]] %>% as.character()
Results = ClimWin[[n]]$Dataset ; head(Results, n = 4)
```
```{r}
ClimVar = "SST" # <- This need to be change
png(file = str_glue("{ClimVar}plotdelta.png"), width=400, height=300)
plotdelta(dataset = Results)
dev.off()
png(file = str_glue("{ClimVar}plotweights.png"), width=400, height=300)
plotweights(dataset = Results)
dev.off()

summary(ClimWin[[n]]$BestModel)
rms::vif(ClimWin[[n]]$BestModel)
```

#### Extract data 
```{r}
ClimateData = ClimWin[[n]]$BestModelData; head(ClimateData)
ExtractedData = ClimateDat = ClimateData %>% select(contains("climate")) %>% rename(!!ClimVar := climate) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^2\\)")), ~ paste0(ClimVar, "_2")) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^3\\)")), ~ paste0(ClimVar, "_3")) %>% 
  bind_cols(Bio)
write_csv(ExtractedData, str_glue("WinHA{ClimVar}.csv"))
```
### Randomization
```{r message=TRUE, results=TRUE, cache=TRUE}
ClimRand <- randwin(repeats = 15,
                    xvar = list(ClimVar = Clim$SST),
                    cdate = Clim$Date,
                    bdate = Bio$DATEmax,
                    baseline = glm(HA ~ PROPORTIONALRANK + AGEHEMB,
                                      family = poisson, 
                                      #nAGQ=0,
                                      data = Bio),
                    cinterval = "week",
                    range = c(10, 0),
                    type = "relative",
                    stat = tidy_stat,
                    func = tidy_func,
                    cmissing = "method1")
```



### Results of randomization
```{r, fig.height = 5, fig.width = 8, fig.align="center"}
ClimWinRand = ClimRand[[1]]

# Diagnostic Plots

pvalue(Results, ClimWinRand, metric = "C", sample.size = 32)

png(file = str_glue("{ClimVar}plothist.png"), width=400, height=300)
plothist(Results, ClimWinRand)
dev.off()
```


# Finding window for Rain
```{r}
# Climatic data
Clim = ClimData %>% 
  select(Date , Area_Rain) %>% # <- This need to be change fo analyse rain
  na.omit()
```

### Climwin Area_Rain
```{r message=TRUE, results=TRUE, cache=TRUE}
ClimWin = slidingwin(xvar = list(ClimVar = Clim$Area_Rain), # <- This need to be change
                     cdate = Clim$Date,
                     bdate = Bio$DATEmax,
                     baseline = glm(HA ~ PROPORTIONALRANK + AGEHEMB,
                                      family = poisson, 
                                      #nAGQ=0,
                                      data = Bio),
                     cinterval = "week",
                     range = c(10, 0), # max window used is 10   
                     type = "relative",
                     stat = c("min", "max", "sum"),# error with min/quad
                     func = c("lin", "quad"), # We can't test with inv and log because of zeros 
                     cmissing = "method1")
```
convergence problem with nAGQ=1

```{r}
Comb = (ClimWin$combos) %>% add_rownames() %>% arrange((DeltaAICc)); Comb
```
```{r}
n = Comb %>% .[[1,1]] %>% as.numeric()
tidy_stat = Comb %>% .[[1, 5]] %>% as.character()
tidy_func = Comb %>% .[[1, 6]] %>% as.character()
Results = ClimWin[[n]]$Dataset ; head(Results, n = 4)
```
```{r}
ClimVar = "Area_Rain" # <- This need to be change 
png(file = str_glue("{ClimVar}plotdelta.png"), width=400, height=300)
plotdelta(dataset = Results)
dev.off()
png(file = str_glue("{ClimVar}plotweights.png"), width=400, height=300)
plotweights(dataset = Results)
dev.off()

summary(ClimWin[[n]]$BestModel)
rms::vif(ClimWin[[n]]$BestModel)
```

#### Extract data 
```{r}
ClimateData = ClimWin[[n]]$BestModelData; head(ClimateData)
ExtractedData = ClimateData %>% select(contains("climate")) %>% rename(!!ClimVar := climate) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^2\\)")), ~ paste0(ClimVar, "_2")) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^3\\)")), ~ paste0(ClimVar, "_3")) %>% 
  bind_cols(Bio)
write_csv(ExtractedData, str_glue("WinHA{ClimVar}.csv"))
```

### Randomization
```{r message=TRUE, results=TRUE, cache=TRUE}
ClimRand <- randwin(repeats = 15,
                    xvar = list(ClimVar = Clim$Area_Rain), # <- This need to be change 
                    cdate = Clim$Date,
                    bdate = Bio$DATEmax,
                    baseline = glm(HA ~ PROPORTIONALRANK + AGEHEMB,
                                      family = poisson, 
                                      #nAGQ=0,
                                      data = Bio),
                    cinterval = "week",
                    range = c(10, 0),
                    type = "relative",
                    stat = tidy_stat,
                    func = tidy_func,
                    cmissing = "method1")
```



### Results of randomization
```{r, fig.height = 5, fig.width = 8, fig.align="center"}
ClimWinRand = ClimRand[[1]]

# Diagnostic Plots

pvalue(Results, ClimWinRand, metric = "C", sample.size = 32)

png(file = str_glue("{ClimVar}plothist.png"), width=400, height=300)
plothist(Results, ClimWinRand)
dev.off()
```


# New data complilation
```{r message=FALSE}
SST <- read_csv("WinHASST.csv") %>% select(1:2, NIDO, WORKYEAR)
Area_Rain <- read_csv("WinHAArea_Rain.csv") %>% select(1:2, NIDO, WORKYEAR)

BioMother <- read.csv("BioWinHA.csv", header = T, sep = ",", stringsAsFactors = F)

FinalData <- plyr::join_all(list(BioMother, SST, Area_Rain), by = c("NIDO", "WORKYEAR"), type = "left") 

write_csv(FinalData, "DATAWinHA.csv")
```

# Which variables need to be refitted? and check colinearity
```{r}
Final_Data = read.csv("DATAWinHA.csv",
                      header = T, sep = ",", stringsAsFactors = F) 
HA_Data <- Final_Data %>% 
  # mutate(across(c(AGEHEMB, SST, Area_Rain), arm::rescale)) %>% 
  mutate(across(c(WORKYEAR, ANILLOHEMB), as.factor)) %>% 
  select(WORKYEAR, HA,
         ANILLOHEMB, AGEHEMB, 
         SST,  
         Area_Rain) %>% 
  drop_na() %>% 
  glimpse()

```

# CLMM
```{r eval=FALSE}
ModClmm = clmm(factor(HA) ~ 
                SST +
                Area_Rain + 
                # AGEHEMB +
                (1|WORKYEAR),
              data = HA_Data)

summary(ModClmm)
confint(ModClmm)



check_collinearity(ModClmm)
```

# Recheck collinearity
```{r}
HA_Data %>% 
  select_if(is.numeric) %>% na.omit() %>% GGally::ggcorr()
```




# Refiting Variables (Chl, SST, Area_Rain_2)
### Data For refitting

```{r, message=FALSE}
BioData = read.csv("DATAWinHA.csv",
                      header = T, sep = ",", stringsAsFactors = F) %>%
  select(DATEmax, NIDO, WORKYEAR, ANILLOHEMB, PROPORTIONALRANK, AGEHEMB, HA, SST, Area_Rain) %>%
  mutate(across(c(DATEmax), ymd))
```

# Climatic data
```{r}
ClimData = read.csv(str_glue("C:/Users/{path}/Dropbox/PHD/DATA/Weather.csv"), sep = ",", header = T,stringsAsFactors = F) %>% 
  rename(Date = time, SST = sst, Area_Rain = rain) %>% mutate(Date = ymd(Date)) %>% 
  select(Date, SST, Area_Rain) 

```




# Reffiting SST

```{r}
Bio = BioData %>% filter(WORKYEAR >= "1989") %>%
  mutate(across(c(WORKYEAR, ANILLOHEMB), as.factor)) %>%
  na.omit() %>% glimpse()

```


```{r}
# Impute manually missing data
# Missing <- c("33/1988", "37/1991", "37/1992",
#              "41/1994", "15/1997", "18/2001",
#              "50/2001", "16/2002", "35/2004",
#              "5/2012", "50/2012", "8/2013",
#              "36/2013", "51/2017")
# 
# Missing_data <- as.Date(paste0('1/', Missing), '%u/%U/%Y')

Clim = ClimData %>% select(Date , SST) %>% drop_na()
  # rbind(., data.frame(Date = Missing_data, SST = NA)) %>% # add missing values
  # arrange(Date) %>%
  # mutate(SST = if_else(is.na(SST), (lag(SST,1) + lead(SST,1) + lag(SST, 2) + lead(SST, 2))/4, SST)) %>%
  # distinct(Date, .keep_all = T)

```

##Climwin analysis

```{r, message=FALSE, results=FALSE, warning=TRUE, cache=TRUE}
ClimWin <- slidingwin(xvar = list(ClimVar = Clim$SST), # Climatic variable
                      cdate = Clim$Date,
                      bdate = Bio$DATEmax,
                      baseline = glm(HA ~ PROPORTIONALRANK + AGEHEMB + Area_Rain,
                                      family = poisson,
                                      # nAGQ=0,
                                      data = Bio),
                      cinterval = "week",
                      range = c(10, 0),
                      type = "relative",
                      stat = c("mean", "min", "max"),
                      func = c("quad", "lin"),
                      cmissing = "method1")

```

### Results

```{r}
Comb = (ClimWin$combos) %>% rownames_to_column() %>% arrange((DeltaAICc)); as.data.frame(Comb)
```


```{r, fig.height = 5, fig.width = 8, fig.align="center"}
n = Comb %>% .[[1,1]] %>% as.numeric()
tidy_stat = Comb %>% .[[1, 5]] %>% as.character()
tidy_func = Comb %>% .[[1, 6]] %>% as.character()
Results = ClimWin[[n]]$Dataset ; head(Results, n = 4)
```
```{r}
ClimVar = "RefittedSST"
png(file = str_glue("{ClimVar}plotdelta.png"), width=400, height=300)
plotdelta(dataset = Results)
dev.off()
png(file = str_glue("{ClimVar}plotweights.png"), width=400, height=300)
plotweights(dataset = Results)
dev.off()

summary(ClimWin[[n]]$BestModel)
rms::vif(ClimWin[[n]]$BestModel)
```

#### Average results
```{r, eval=TRUE}
# Only one window explain 95% of the variation we don't need to average the result
# calculate mean open window and mean close window from the best model base on the 95% confidence
medwin(ClimWin[[n]]$Dataset) # calculate mean open window and mean close window from the best model base on the 95% confidence

dataset <- ClimWin[[n]]$Dataset

ConfidenceSet <- dataset[which(cumsum(dataset$ModWeight) <= 0.95), ]

sum(ConfidenceSet$ModelBeta*ConfidenceSet$ModWeight)

```

#### Extract data RefittedSST
```{r}
ClimateData = ClimWin[[n]]$BestModelData; head(ClimateData)
Area_RainData = ClimateData %>% select(contains("climate")) %>% rename(!!ClimVar := climate) %>%
  rename_if((str_detect(names(.), "I\\(climate\\^2\\)")), ~ paste0(ClimVar, "_2")) %>%
  rename_if((str_detect(names(.), "I\\(climate\\^3\\)")), ~ paste0(ClimVar, "_3")) %>%
  bind_cols(Bio)
write_csv(Area_RainData, str_glue("WinHA{ClimVar}.csv"))
```
## Randomization
```{r, message=FALSE, results=FALSE, warning=TRUE, cache=TRUE}
ClimRand <- randwin(repeats = 15,
                    xvar = list(ClimVar = Clim$SST),
                    cdate = Clim$Date,
                    bdate = Bio$DATEmax,
                    baseline = glm(HA ~ PROPORTIONALRANK + AGEHEMB + Area_Rain,
                                   family = poisson,
                                   # nAGQ=0,
                                   data = Bio),
                    cinterval = "week",
                    range = c(10, 0),
                    type = "relative",
                    stat = tidy_stat,
                    func = tidy_func,
                    cmissing = "method1")

```



### Results of randomization
```{r, fig.height = 5, fig.width = 8, fig.align="center"}
ClimWinRand = ClimRand[[1]]

# Diagnostic Plots

pvalue(Results, ClimWinRand, metric = "C", sample.size = 32)

png(file = str_glue("{ClimVar}plothist.png"), width=400, height=300)
plothist(Results, ClimWinRand)
dev.off()
```


## Weight SST
```{r, eval=TRUE, cache=TRUE, results="hide", message=FALSE}
# Bio_Scale <- Bio %>% mutate(across(c(HatchAsync, PROPORTIONALRANK, SST), scale))
# Clim_Scale <- Clim %>% mutate(across(c(Chl), scale))
dev.new(noRStudioGD = T)
weight <- weightwin(n = 15,
                    xvar = list(ClimVar = Clim$SST),
                    cdate = Clim$Date,
                    bdate = Bio$DATEmax,
                    baseline = glm(HA ~ PROPORTIONALRANK + AGEHEMB + Area_Rain,
                                   family = poisson,
                                   # nAGQ=0,
                                   data = Bio),
                    cinterval = "week",
                    range = c(10, 0),
                    type = "relative",
                    func = tidy_func,
                    weightfunc = "W",
                    cmissing = "method1",
                    par = c(3, 0.2, 0))

```
#### Weight SST results
```{r}
Weight_results <- weight$iterations %>% rownames_to_column() %>% arrange(deltaAICc); Weight_results # Show iteration results
n <- Weight_results[1, 1] %>% as.numeric()
Best_iter <- weight[[n]]$WeightedOutput; Best_iter # Best model interation
```


```{r, warning=TRUE}
png(file = str_glue("{ClimVar}Weights.png"), width=400, height=300)
plot(weight[[n]]$Weights, type = "line")
dev.off()
```
We need to compare the AIC from the slidingwin function and from the weightwin to see with function explain better the variation in brood reduction either a weight with uniform distribution or a weight with Weibull distribution.
Here we can se that the better model is with _..._ function

### Randomization weight
```{r, eval=FALSE, cache=TRUE, results="hide", message=FALSE}
dev.new(noRStudioGD = T)
WeightRand <- randwin(repeats = 15,
                      window = "weighted",
                      xvar = list(ClimVar = Clim$SST),
                      cdate = Clim$Date,
                      bdate = Bio$DATEmax,
                      baseline = glm(HA ~ PROPORTIONALRANK + AGEHEMB + Area_Rain,
                                     family = poisson,
                                     # nAGQ=0,
                                     data = Bio),
                      cinterval = "week",
                      range = c(10, 0),
                      type = "relative",
                      func = tidy_func,
                      weightfunc = "W",
                      cmissing = "method1",
                      par = c(3, 0.2, 0))

```

#### Results weight
```{r eval=FALSE}
pvalue(dataset = weight[[n]]$WeightedOutput, datasetrand = WeightRand[[1]], metric = "AIC")
```




# Reffiting Area Rain

```{r}
Clim = ClimData %>% select(Date , Area_Rain) %>%
  na.omit()
```

##Climwin analysis

```{r, message=FALSE, results=FALSE, warning=TRUE, cache=TRUE}
ClimWin <- slidingwin(xvar = list(ClimVar = Clim$Area_Rain), # Climatic variable
                      cdate = Clim$Date,
                      bdate = Bio$DATEmax,
                      baseline = glm(HA ~ PROPORTIONALRANK + AGEHEMB + SST + I(SST^2),
                                     family = poisson,
                                     # nAGQ=0,
                                     data = Bio),
                      cinterval = "week",
                      range = c(10, 0),
                      type = "relative",
                      stat = c("max", "sum", "min"),
                      func = c("quad", "lin"),
                      cmissing = "method1")
```

### Results

```{r}
Comb = (ClimWin$combos) %>% rownames_to_column() %>% arrange((DeltaAICc)); as.data.frame(Comb)
```


```{r, fig.height = 5, fig.width = 8, fig.align="center"}
n = Comb %>% .[[1,1]] %>% as.numeric()
tidy_stat = Comb %>% .[[1, 5]] %>% as.character()
tidy_func = Comb %>% .[[1, 6]] %>% as.character()
Results = ClimWin[[n]]$Dataset ; head(Results, n = 4)
```
```{r}
ClimVar = "RefittedArea_Rain"
png(file = str_glue("{ClimVar}plotdelta.png"), width=400, height=300)
plotdelta(dataset = Results)
dev.off()
png(file = str_glue("{ClimVar}plotweights.png"), width=400, height=300)
plotweights(dataset = Results)
dev.off()

summary(ClimWin[[n]]$BestModel)
rms::vif(ClimWin[[n]]$BestModel)
```

#### Average results
```{r}
medwin(ClimWin[[n]]$Dataset) # calculate mean open window and mean close window from the best model base on the 95% confidence

dataset <- ClimWin[[n]]$Dataset

ConfidenceSet <- dataset[which(cumsum(dataset$ModWeight) <= 0.95), ]

sum(ConfidenceSet$ModelBeta*ConfidenceSet$ModWeight)
```


#### Extract data Refitted Area Rain
```{r}
ClimateData = ClimWin[[n]]$BestModelData; head(ClimateData)
Area_RainData = ClimateData %>% select(contains("climate")) %>% rename(!!ClimVar := climate) %>%
  rename_if((str_detect(names(.), "I\\(climate\\^2\\)")), ~ paste0(ClimVar, "_2")) %>%
  rename_if((str_detect(names(.), "I\\(climate\\^3\\)")), ~ paste0(ClimVar, "_3")) %>%
  bind_cols(Bio)
write_csv(Area_RainData, str_glue("WinHA{ClimVar}.csv"))
```
## Randomization
```{r, message=FALSE, results=FALSE, warning=TRUE, cache=TRUE}
ClimRand <- randwin(repeats = 15,
                    xvar = list(ClimVar = Clim$Area_Rain),
                    cdate = Clim$Date,
                    bdate = Bio$DATEmax,
                    baseline = glm(HA ~ PROPORTIONALRANK + AGEHEMB + SST + I(SST^2),
                                   family = poisson,
                                   # nAGQ=0,
                                   data = Bio),
                    cinterval = "week",
                    range = c(10, 0),
                    type = "relative",
                    stat = tidy_stat,
                    func = tidy_func,
                    cmissing = "method1")
```



### Results of randomization
```{r, fig.height = 5, fig.width = 8, fig.align="center"}
ClimWinRand = ClimRand[[1]]

# Diagnostic Plots

pvalue(Results, ClimWinRand, metric = "C", sample.size = 32)

png(file = str_glue("{ClimVar}plothist.png"), width=400, height=300)
plothist(Results, ClimWinRand)
dev.off()
```

### Weight Area_Rain_2
```{r, eval=TRUE, cache=TRUE, results="hide", message=FALSE}
# Bio_Scale <- Bio %>% mutate(across(c(HatchAsync, PROPORTIONALRANK, SST), scale))
# Clim_Scale <- Clim %>% mutate(across(c(Chl), scale))
dev.new(noRStudioGD = T)
weight <- weightwin(n = 15,
                    xvar = list(ClimVar = Clim$Area_Rain),
                    cdate = Clim$Date,
                    bdate = Bio$DATEmax,
                    baseline = glm(HA ~ PROPORTIONALRANK + AGEHEMB + SST + I(SST^2),
                                   family = poisson,
                                   # nAGQ=0,
                                   data = Bio),
                    cinterval = "week",
                    range = c(10, 0),
                    type = "relative",
                    func = tidy_func,
                    weightfunc = "W",
                    cmissing = "method1",
                    par = c(3, 0.2, 0))
```
#### Weight Area_Rain_2 results
```{r}
Weight_results <- weight$iterations %>% rownames_to_column() %>% arrange(deltaAICc); Weight_results # Show iteration results
n <- Weight_results[1, 1] %>% as.numeric()
Best_iter <- weight[[n]]$WeightedOutput; Best_iter # Best model interation
```


```{r, warning=TRUE}
png(file = str_glue("{ClimVar}Weights.png"), width=400, height=300)
plot(weight[[n]]$Weights, type = "line")
dev.off()
```
We need to compare the AIC from the slidingwin function and from the weightwin to see with function explain better the variation in brood reduction either a weight with uniform distribution or a weight with Weibull distribution.
Here we can se that the better model is with _..._ function

### Randomization weight
```{r, eval=TRUE, cache=TRUE, results="hide", message=FALSE}
dev.new(noRStudioGD = T)
WeightRand <- randwin(repeats = 15,
                      window = "weighted",
                      xvar = list(ClimVar = Clim$Area_Rain),
                      cdate = Clim$Date,
                      bdate = Bio$DATEmax,
                      baseline = glm(HA ~ PROPORTIONALRANK + AGEHEMB + SST + I(SST^2),
                                     family = poisson,
                                     # nAGQ=0,
                                     data = Bio),
                      cinterval = "week",
                      range = c(10, 0),
                      type = "relative",
                      func = tidy_func,
                      cmissing = "method1",
                      weightfunc = "W", par = c(3, 0.2, 0))

```

#### Results weight
```{r}
pvalue(dataset = weight[[n]]$WeightedOutput, datasetrand = WeightRand[[1]], metric = "AIC")
```




# Final compilation of data
```{r, results=FALSE, message=FALSE}
# Compile new data
RefittedSST = read_csv("WinHARefittedSST.csv") %>%
  select(1:2, NIDO, WORKYEAR)
RefittedArea_Rain = read_csv("WinHARefittedArea_Rain.csv") %>%
  select(1:2, NIDO, WORKYEAR)

BioMother <- read.csv("BioWinHA.csv", header = T, sep = ",",
                   stringsAsFactors = F)

FinalData = plyr::join_all(list(BioMother, RefittedSST, RefittedArea_Rain),
                           by = c("NIDO", "WORKYEAR"),
                           type = "left") %>% glimpse()
write_csv(FinalData, "RefittedDATAHASize.csv")
```






# Performing analysis

```{r}
Data <- read.csv("RefittedDATAHASize.csv", header = T, sep = ",",
                 stringsAsFactors = F)
Data_HA <- Data %>%
  filter(!ANILLOHEMB == "SA") %>%
  select(NIDO, WORKYEAR, HA,
         ANILLOHEMB, AGEHEMB,
         PROPORTIONALRANK,
         RefittedSST, RefittedArea_Rain) %>%
  mutate(across(c(WORKYEAR), as.character)) %>%
  # mutate(across(c(where(is.numeric), -HA), arm::rescale)) %>%
  mutate(across(c(where(is.character)), as.factor)) %>%
  drop_na() %>%
  glimpse()

SampleSize_nests <- Data_HA %>% count() %>% pull()
SampleSize_females <- Data_HA %>% count(ANILLOHEMB) %>% count() %>% pull()
SampleSize_females
Data_HA %>% ggplot(aes(HA)) + geom_bar()
```
## Clmm model
```{r}
ModClmm = clmm(factor(HA) ~
                 RefittedSST + #I(RefittedSST^2) +
                 PROPORTIONALRANK + #I(PROPORTIONALRANK^2) +
                 RefittedArea_Rain +
                 AGEHEMB +
                 (1|WORKYEAR) + (1|ANILLOHEMB),
               data = Data_HA)

summary <- summary(ModClmm); summary

```
No sign interaction: PROP:SST and PROP:HEMB
exp(-1.00038) = 0.367, which means that at each increase in SST female have a (1 - 0.367) = 63% lower odds of being less likely to apply lay a larger clutch size.

In other words likelihood of a clutch of 2 versus a clutch of 1 on the rating scale is multiplied by 0.3677

exp(0.40742) = 1.502935, which means that at each increase in SST female have a (1 - 1.502935) = -50% odds to hatch the clutch at higher intervals of asynchrony.

In other words likelihood of a clutch with a HA of 3 versus a clutch of 3>HA<9 on the rating scale is multiplied by 1.502935

### Create FINAL clmm table
```{r eval=TRUE}
# Table to results coef
FixCoef <- broom::tidy(ModClmm)
RanCoef <- data.frame(Term = c("Year", "Female ID"),
                      Std.Dev. = c(summary$ST$WORKYEAR[[1]],
                                   summary$ST$ANILLOHEMB[[1]]
                      )) %>%
  mutate(Variance = Std.Dev.^2)

CI <- confint(ModClmm, level = 0.95)

CoefCLMMTable <- FixCoef %>% bind_cols(as.data.frame(CI))

write_csv(CoefCLMMTable, "Climwin_CLMM_fixcoef.csv")
write_csv(RanCoef, "Climwin_CLMM_rancoef.csv")
```

# Plot
```{r}
Data_HA$fitted <- fitted(ModClmm)
plot(fitted~RefittedSST, data=Data_HA)
```



<!-- ```{r, eval=FALSE} -->
<!-- check_collinearity(ModClmm) -->
<!-- ``` -->



<!-- ### Create clmm plot -->
<!-- ```{r} -->
<!-- fitChl <- fitted(ModClmm) %>% bind_cols(Data_HA$RefittedSST) %>% -->
<!--   rename(fit = `...1`, chl =`...2`) -->
<!-- fitChl %>% ggplot(aes(chl, fit)) + geom_point() -->
<!-- ``` -->


<!-- ## Normal distribution -->
<!-- ```{r} -->
<!-- ModLmer = lmer(as.numeric(HA) ~ -->
<!--                  RefittedSST +  -->
<!--                  RefittedArea_Rain + I(RefittedArea_Rain^2) + -->
<!--                  PROPORTIONALRANK + -->
<!--                  AGEHEMB + -->
<!--                  (1|WORKYEAR), -->
<!--                na.action = "na.fail", -->
<!--                REML = F, -->
<!--                data = Data_HA) -->

<!-- # Results LMM -->
<!-- LmmConfint <- confint(ModLmer) %>% as.data.frame() %>% dplyr::slice(-(1:2)) -->

<!-- Lmmsummary <- summary(ModLmer)[["coefficients"]] %>% as.data.frame() %>% bind_cols(LmmConfint) %>% -->
<!--   rownames_to_column("Predictor") %>% -->
<!--   rename(`IC 2.5%` = `2.5 %`, `IC 97.5%` = `97.5 %`) %>% -->
<!--   mutate(across(c(where(is.numeric)), ~round(., 2))); Lmmsummary -->

<!-- ``` -->

<!-- ### Model selection -->
<!-- ```{r, eval=FALSE, echo=FALSE} -->
<!-- # With Dredge -->
<!-- drg <- MuMIn::dredge(ModLmer) -->
<!-- head(drg, n = 10) -->
<!-- delta2=MuMIn::get.models(drg,subset= delta < 2) -->
<!-- summary(MuMIn::model.avg(delta2)) -->
<!-- ``` -->

<!-- ```{r, eval=FALSE, echo=FALSE} -->
<!-- # Without dregde -->
<!-- Rand0 <- lm(HA ~ RefittedSST + I(RefittedSST^2) + -->
<!--                  RefittedArea_Rain + I(RefittedArea_Rain^2) + -->
<!--                  LastNDepredationYear + -->
<!--                  CoupleExpLocal + -->
<!--                  AGEHEMB, -->
<!--                data = Data_HA) -->
<!-- RandRing <- (update(ModLmer, . ~ . -(1|WORKYEAR))) -->
<!-- RandYear <- (update(ModLmer, . ~ . -(1|ANILLOHEMB))) -->
<!-- bbmle::AICtab(Rand0, RandRing, RandYear, ModLmer) -->
<!-- anova(ModLmer, RandRing) -->

<!-- ``` -->


<!-- ### LMM Diagnostic -->
<!-- ```{r} -->
<!-- #Collinearity -->
<!-- check_collinearity(ModClmm) -->
<!-- # Diagnostics -->
<!-- ## Linearity -->
<!-- plot(resid(ModLmer),fitted(ModLmer)) -->
<!-- # plot(resid(ModLmer), HA_Data) error -->
<!-- ## Homogeneity -->
<!-- plot(ModLmer) -->
<!-- ## Normality -->
<!-- qqnorm(residuals(ModLmer)) -->
<!-- # qqline(resid(ModLmer)) -->
<!-- ``` -->



<!-- ### Plots -->
<!-- ```{r} -->
<!-- # With effect package -->
<!-- plot(allEffects(ModLmer, residuals=TRUE)) -->


<!-- ef <- effect("RefittedSST", ModLmer) -->
<!-- x <- as.data.frame(ef) -->
<!-- summary(x) -->
<!-- ggplot(x, aes(RefittedSST, fit)) + geom_line() + -->
<!--   geom_smooth(aes(ymin=lower, ymax=upper), stat = "identity", alpha = 0.3) + -->
<!--   theme_fivethirtyeight() + -->
<!--   theme(axis.title = element_text(), -->
<!--         plot.caption = element_text(size = 15, hjust = 0), -->
<!--         plot.background = element_rect(fill = "white"), -->
<!--         panel.background = element_rect(fill = "white"), -->
<!--         legend.background = element_rect(fill = "white")) + -->
<!--   scale_x_continuous(n.breaks = 10) + -->
<!--   scale_y_continuous(n.breaks = 10) + -->
<!--   scale_fill_manual(values =  c("#a60019" ,"#009dab")) + -->
<!--   scale_color_manual(values = c("#a60019" ,"#009dab")) + -->
<!--   labs(x = "RefittedSST", y = "HA", -->
<!--        caption = "Graph of the HA in function of chlorophyll-a concentration") -->

<!-- # ggsave(filename = "C:/Users/ivan/Dropbox/PHD/Plots/rplot.png", width = 9, height = 6) -->
<!-- ``` -->
<!-- ```{r eval=FALSE} -->
<!-- # Create new data -->
<!-- names(Data_HA) -->
<!-- Data_HA %>% select(RefittedSST) %>% ggplot(aes(RefittedSST)) + geom_histogram() + scale_x_continuous(n.breaks = 20) -->
<!-- set.seed(123) -->
<!-- RandomYear <- Data_HA %>% select(WORKYEAR) %>% sample_n(1) %>% pull() %>% droplevels() -->
<!-- RandomRing <- Data_HA %>% select(ANILLOHEMB) %>% sample_n(1) %>% pull() %>% droplevels() -->
<!-- Newdata <- expand_grid(WORKYEAR = RandomYear, ANILLOHEMB = RandomRing, -->
<!--                        AGEHEMB = mean(Data_HA$AGEHEMB), -->
<!--                        PROPORTIONALRANK = mean(Data_HA$PROPORTIONALRANK), -->
<!--                        CoupleExpLocal = mean(Data_HA$CoupleExpLocal), -->
<!--                        RefittedArea_Rain = mean(Data_HA$RefittedArea_Rain), -->
<!--                        RefittedSST = mean(Data_HA$RefittedSST), -->
<!--                        LastDepredRate = 0) -->


<!-- predChl <- predict(ModLmer, Newdata, re.form=NA) -->

<!-- pfun <- function(fit) { -->
<!--     predict(fit, newdata=Newdata, re.form=NA) -->
<!-- } -->
<!-- cc <- confint(ModLmer,method="boot",FUN=pfun) -->
<!-- Predic <- Newdata %>% select(RefittedSST) %>% bind_cols(predChl, as.data.frame(cc)) %>% rename(fit = `...2`, lwr = `2.5 %`, upr =  `97.5 %`) -->
<!-- Predic %>% ggplot(aes(RefittedSST, fit)) + -->
<!--   geom_ribbon(aes(ymin = lwr, ymax = upr), fill = "grey70") + -->
<!--   geom_line() + geom_point(data = Data_HA, aes(RefittedSST, Clutch)) -->
<!-- ``` -->


<!-- ```{r, eval=FALSE, echo=FALSE} -->
<!-- # Alternative way -->
<!-- ChlIC <- merTools::predictInterval(ModLmer, Newdata, n.sims = 50) -->
<!-- ChlBootIC <- bootMer(ModLmer, FUN = function(x) predict(ModLmer, Newdata, re.form=NA),nsim=15) -->
<!-- #extract the quantiles and the fitted values. -->
<!-- lci <- apply(ChlBootIC$t, 2, quantile, 0.025) -->
<!-- uci <- apply(ChlBootIC$t, 2, quantile, 0.975) -->

<!-- Pred <- Newdata %>% select(RefittedSST) %>% bind_cols(predChl, lci, uci) %>% rename(fit = `...2`, lwr = `...3`, upr =  `...4`) -->


<!-- Predictions <- ChlIC %>% bind_cols(Newdata %>% select(RefittedSST)) -->
<!-- newdata$predFE = Chl$fit -->
<!-- newdata$predFE.min = Chl$fit-1.98*Chl$se.fit -->
<!-- newdata$predFE.max = Chl$fit+1.98*Chl$se.fit -->
<!-- real=ddply(DATAsurv, ~ Status + RainYear+ #AGEHEMB + -->
<!--              PROPORTIONALRANK + SSTYear + #BroodReduction+ -->
<!--              WORKYEAR + NIDO, summarize, m=mean(EMPLUMA)) -->

<!-- Predi %>% ggplot(aes(RefittedSST, fit)) + -->
<!--   geom_ribbon(aes(ymin = lwr, ymax = upr), fill = "grey70") + -->
<!--   geom_line() -->
<!--   # geom_point(data=real, aes(x=Status, y=m) )+ -->
<!--   # ylab("Average probability of survival")+ -->
<!--   # xlab("Status") -->
<!-- ``` -->


<!-- ## Bernouilli distribution -->
<!-- ```{r eval=FALSE} -->
<!-- Bin_HA <- Data_HA %>% mutate(HA = case_when(HA == 0 ~ 0, -->
<!--                                           HA >= 3 ~ 1)) %>% -->
<!--   drop_na() -->

<!-- ModLg = glmmTMB(HA ~ -->
<!--                  RefittedSST + I(RefittedSST^2) + -->
<!--                  RefittedArea_Rain + I(RefittedArea_Rain^2) + -->
<!--                  # CoupleExpLocal + -->
<!--                  # LastDepredRate + -->
<!--                  PROPORTIONALRANK + -->
<!--                  AGEHEMB + -->
<!--                  (1|WORKYEAR), -->
<!--                 family = binomial(link = "logit"), -->
<!--                 ziformula = ~0, -->
<!--                 REML = F, -->
<!--                 data = Bin_HA) -->

<!-- summary(ModLg) -->
<!-- check_collinearity(ModLg) -->

<!-- # Diagnostics -->
<!-- resbi = simulateResiduals(ModLg) -->
<!-- plot(resbi) -->
<!-- testDispersion(resbi) -->
<!-- testUniformity(resbi) -->
<!-- testOutliers(resbi) -->
<!-- testQuantiles(resbi) -->
<!-- testZeroInflation(resbi) -->

<!-- ``` -->



## Poisson distribution
```{r, eval=FALSE, echo=FALSE}
# Poisson distribution
var(Data_HA$HA) #  mean /= variance we don't need to use quasi poisson
mean(Data_HA$HA)

ModGlmm = glmmTMB(HA ~ 
                 RefittedSST + #I(RefittedSST^2) +
                 PROPORTIONALRANK + #I(PROPORTIONALRANK^2) +
                 RefittedArea_Rain +
                 AGEHEMB +
                 (1|WORKYEAR) + (1|ANILLOHEMB),
                  family = poisson,
                  ziformula = ~0,
                  REML = F,
                  data = Data_HA)
ModGlmm1 <- update(ModGlmm, . ~ ., ziformula = ~1)
ModGlmm. <- update(ModGlmm, . ~ ., ziformula = ~.)
ModGlmmnb1 <- update(ModGlmm, . ~ ., family = nbinom1)
ModGlmmnb2 <- update(ModGlmm, . ~ ., family = nbinom2)
# ModGlmmTnb1 <- update(ModGlmm, . ~ ., family = truncated_nbinom1)
# ModGlmmTnb2 <- update(ModGlmm, . ~ ., family = truncated_nbinom2)
ModGlmmnb2zi1 <- update(ModGlmm, . ~ ., family = nbinom2, ziformula = ~1)
bbmle::AICtab(ModGlmm., ModGlmm1, ModGlmm, ModGlmmnb1, ModGlmmnb2, ModGlmmnb2zi1)

summary(ModGlmm)
check_collinearity(ModGlmm)

plot(allEffects(ModGlmm))
```
<!-- ```{r, eval=FALSE, echo=FALSE} -->
<!-- # Diagnostics -->
<!-- res = simulateResiduals(ModGlmm) -->
<!-- plot(res) -->
<!-- testDispersion(res) -->
<!-- testUniformity(res) -->
<!-- testOutliers(res) -->
<!-- testQuantiles(res) -->
<!-- testZeroInflation(res) -->
<!-- ``` -->


<!-- Negative binomial distribution -->
<!-- ```{r, eval=FALSE, echo=FALSE} -->
<!-- ModNB = glm(HA ~ PROPORTIONALRANK + -->
<!--               # RefittedChl + I(RefittedChl^2) + -->
<!--               RefittedSST + #I(RefittedSST^2) + -->
<!--               # RefittedArea_Rain + I(RefittedArea_Rain^2) + -->
<!--               # CoupleExpLocal + -->
<!--               # CoupleExpLocal + -->
<!--               AGEHEMB, -->
<!--             (1|WORKYEAR), -->
<!--             family = poisson(link = log), -->
<!--             data = Data_HA) -->

<!-- summary(ModNB) -->
<!-- ModGlmm.nb <- glmer.nb(formula(ModGlmm), data = Data_HA) -->

<!-- autoplot(countreg::rootogram(ModTruc, scale = "raw")) -->
<!-- ``` -->
## Truncated poisson
```{r, eval=FALSE, echo=FALSE}
ModTrunc = glmmTMB(HA ~ PROPORTIONALRANK +
                    RefittedSST + #I(RefittedSST^2) +
                    RefittedArea_Rain + #I(RefittedArea_Rain^2) +
                    AGEHEMB +
                    (1|WORKYEAR) + (1|ANILLOHEMB),
                  family = "truncated_poisson"(link = "log"),
                  ziformula = ~0,
                  REML = F,
                  data = Data_HA)
bbmle::AICtab(ModGlmm, ModTrunc)

summary(ModTrunc)
# Idem results with vgam (but can't add random effects)
```


```{r, eval=FALSE, echo=FALSE}
# Diagnostics
res = simulateResiduals(ModTrunc)
plot(res)
testDispersion(res)
testUniformity(res)
testOutliers(res)
testQuantiles(res)
testZeroInflation(res)
```



<!-- # Performing analysis -->

<!-- ```{r} -->
<!-- Data <- read.csv("RefittedDATAHASize.csv", header = T, sep = ",", -->
<!--                  stringsAsFactors = F) -->
<!-- Data_HA <- Data %>% -->
<!--   filter(CONFIRMMACH == "t") %>% -->
<!--   filter(!ANILLOMACH == "SA") %>% -->
<!--   select(NIDO, WORKYEAR, HA, -->
<!--          ANILLOMACH, RealFatherAge, -->
<!--          PROPORTIONALRANK, -->
<!--          RefittedSST, RefittedArea_Rain) %>% -->
<!--   mutate(across(c(WORKYEAR), as.character)) %>% -->
<!--   mutate(across(c(where(is.numeric), -HA), arm::rescale)) %>% -->
<!--   mutate(across(c(where(is.character)), as.factor)) %>% -->
<!--   drop_na() %>% -->
<!--   glimpse() -->

<!-- SampleSize_nests <- Data_HA %>% count() %>% pull() -->
<!-- SampleSize_males <- Data_HA %>% count(ANILLOMACH) %>% count() %>% pull() -->
<!-- SampleSize_males -->
<!-- Data_HA %>% ggplot(aes(HA)) + geom_bar() -->
<!-- ``` -->
<!-- ## Clmm model -->
<!-- ```{r} -->
<!-- ModClmm = clmm(factor(HA) ~ -->
<!--                  PROPORTIONALRANK + -->
<!--                  RefittedSST +  -->
<!--                  RefittedArea_Rain + I(RefittedArea_Rain^2) + -->
<!--                  RealFatherAge + I(RealFatherAge^2) + -->
<!--                  (1|WORKYEAR) + (1|ANILLOMACH), -->
<!--                data = Data_HA) -->

<!-- summary <- summary(ModClmm); summary -->

<!-- ``` -->



# Plasticity


### Re-Import final data
```{r}
Data <- read.csv("RefittedDATAHASize.csv", header = T, sep = ",",
                 stringsAsFactors = F)
```

### Add plasticity variables
We added to previous models the mean rainfall experienced across all nesting attempts (̄x rainfall ,a single term per individual female), as well as the deviation from the female‐specific mean rainfall for each of her separate nesting attempts (Δ rainfall, a single term per individual nest attempt) to examined their independent effects on success of each reproductive output.
```{r}
Data_HA <- Data %>%
  filter(!ANILLOHEMB == "SA") %>%
  select(NIDO, WORKYEAR, HA,
         RefittedSST,
         RefittedArea_Rain,
         ANILLOHEMB,
         AGEHEMB,
         PROPORTIONALRANK) %>%
  mutate(across(c(WORKYEAR), as.character)) %>%
  mutate(across(where(is.character), as.factor)) %>%
  drop_na() %>%
  group_by(ANILLOHEMB) %>% arrange(ANILLOHEMB) %>%
  mutate(
    meanSST = mean(RefittedSST),
    deltaSST = (RefittedSST - meanSST),
  ) %>%
  mutate(n = n()) %>%
  ungroup() %>%
  # mutate(across(c(where(is.numeric), -HA, -n), arm::rescale)) %>% #DON'T rescale
  filter(n > 1) %>% # Only use birds with multiple reads. This can cause that results may vary respect to previous analysis
  glimpse()

Sample_size_plast_fem <- Data_HA %>% count(ANILLOHEMB) %>% count() %>% pull # half of females reproduced at least 2 or more times
Sample_size_plast_nest <- Data_HA %>% count() %>% pull # half of females reproduced at least 2 or more times

Sample_size_plast_fem
Sample_size_plast_nest
```

## Analysis of plasticity


## Clmm model
```{r}
ModClmm = clmm(factor(HA) ~
                 deltaSST +
                 meanSST + 
                 PROPORTIONALRANK +
                 RefittedArea_Rain +
                 AGEHEMB + 
                 (1|WORKYEAR) + (1|ANILLOHEMB), data = Data_HA)

summary <- summary(ModClmm); summary

check_collinearity(ModClmm)
```

We found that mean chl were not significatif. Meaning that more fecund females were not more likely to lay when chl concentration was high and SST low.

Delta chl was significative meaning that individual females did showed a plastic reproductive response to chl quantity, they did adjust their hatching asincrony to the amount of chl in the ocean.


In conclusion blue footeed boobies don't have a o a very slight plastic response to proxies related to food abundance ajusting hatching asynchrony.

### Export plasticity results
```{r}
# Table <- summary$coefficients %>% cbind(confint(ModClmm))
# write.csv(Table, "Climwin_HASize_Plasticity.csv")

FixCoef <- broom::tidy(ModClmm)
RanCoef <- data.frame(Term = c("Year", "Female ID"),
                      Std.Dev. = c(summary$ST$WORKYEAR[[1]],
                                   summary$ST$ANILLOHEMB[[1]])
                      ) %>%
  mutate(Variance = Std.Dev.^2)

CI <- confint(ModClmm, level = 0.95)

CoefCLMMTable <- FixCoef %>% bind_cols(as.data.frame(CI))

write_csv(CoefCLMMTable, "Climwin_HASize_Plasticity_fix.csv")
write_csv(RanCoef, "Climwin_HASize_Plasticity_ran.csv")

```

<!-- ## Truncated poisson -->
<!-- ```{r, eval=FALSE, echo=FALSE} -->
<!-- ModTrunc = glmmTMB(HA ~ PROPORTIONALRANK + -->
<!--                      meanSST + deltaSST + -->
<!--                      RefittedArea_Rain + I(RefittedArea_Rain^2) + -->
<!--                      AGEHEMB + -->
<!--                      (1|WORKYEAR) + (1|ANILLOHEMB), -->
<!--                    family = "truncated_poisson"(link = "log"), -->
<!--                    ziformula = ~0, -->
<!--                    REML = F, -->
<!--                    data = Data_HA) -->
<!-- bbmle::AICtab(ModGlmm, ModTrunc) -->

<!-- summary(ModTrunc) -->
<!-- # Idem results with vgam (but can't add random effects) -->
<!-- ``` -->

<!-- ## Normal distribution -->
<!-- ```{r eval=FALSE} -->
<!-- ModLmer = lmer(HA ~ -->
<!--                  meanSST + deltaSST + -->
<!--                  RefittedArea_Rain + I(RefittedArea_Rain^2) + -->
<!--                  PROPORTIONALRANK + -->
<!--                  AGEHEMB + -->
<!--                  (1|WORKYEAR) + (1|ANILLOHEMB), -->
<!--                na.action = "na.fail", -->
<!--                REML = F, -->
<!--                data = Data_HA) -->

<!-- # Results LMM -->
<!-- LmmConfint <- confint(ModLmer) %>% as.data.frame() %>% dplyr::slice(-(1:2)) -->
<!-- Lmmsummary <- summary(ModLmer)[["coefficients"]] %>% as.data.frame() %>% bind_cols(LmmConfint) %>% -->
<!--   rownames_to_column("Predictor") %>% -->
<!--   rename(`IC 2.5%` = `2.5 %`, `IC 97.5%` = `97.5 %`) %>% -->
<!--   mutate(across(c(where(is.numeric)), ~round(., 2))); Lmmsummary -->

<!-- ``` -->


## Check significativity between BW and BB

## Clmm model
```{r}
ModClmm = clmm(factor(HA) ~
                 RefittedSST +
                 meanSST + 
                 PROPORTIONALRANK +
                 RefittedArea_Rain + 
                 AGEHEMB + 
                 (1|WORKYEAR) + (1|ANILLOHEMB), data = Data_HA)

summary <- summary(ModClmm); summary
```

We checked if the within-subject effect (bW) or the between-subject effect (bB) are significatively deferents between each other. In both cases Within and between are significatiely diferents meaning that effectively boobies does have a plstic response to chl, and that the between effect is much greater than the within effect.



### Export bB-bW results
```{r}
# Table <- summary$coefficients %>% cbind(confint(ModClmm))
# write.csv(Table, "Climwin_HASize_Plasticity.csv")

FixCoef <- broom::tidy(ModClmm)
RanCoef <- data.frame(Term = c("Year", "Female ID"),
                      Std.Dev. = c(summary$ST$WORKYEAR[[1]],
                                   summary$ST$ANILLOHEMB[[1]])
                      ) %>%
  mutate(Variance = Std.Dev.^2)

CI <- confint(ModClmm, level = 0.95)

CoefCLMMTable <- FixCoef %>% bind_cols(as.data.frame(CI))

write_csv(CoefCLMMTable, "Climwin_HASize_B_W_fix.csv")
write_csv(RanCoef, "Climwin_HASize_B_W_ran.csv")
```





<!-- ### Create FINAL clmm table plasticity -->
<!-- ```{r} -->
<!-- # Table to results coef -->
<!-- FixCoef <- broom::tidy(ModClmm) -->
<!-- RanCoef <- data.frame(Term = c("Year", "Female ID"), -->
<!--                       Std.Dev. = c(summary$ST[[1]], -->
<!--                                    summary$ST[[2]])) %>% -->
<!--   mutate(Variance = Std.Dev.^2) -->

<!-- CI <- confint(ModClmm, level = 0.95) -->

<!-- CoefCLMMTable <- FixCoef %>% bind_cols(as.data.frame(CI)) -->

<!-- write_csv(CoefCLMMTable, "Climwin_CLMM_fixcoef.csv") -->
<!-- write_csv(RanCoef, "Climwin_CLMM_rancoef.csv") -->

<!-- Terms = c("Laying date","$\\beta$b Chl", "$\\beta$w Chl","$\\beta$b SST", "$\\beta$w SST","Rain", "Rain²", "Female age","Female age²") -->

<!-- read.csv("Climwin_HA_Plasticity.csv") %>% -->
<!--   select(-Pr...z..) %>% mutate(across(where(is.numeric), ~round(., digits = 2))) %>% -->
<!--   unite("IC", `X2.5..`:`X97.5..`, sep = " | ") %>% dplyr::slice(-(1:2)) %>% -->
<!--   mutate(X = Terms) %>% -->
<!--   rename(Terms = X) %>% -->
<!--   kbl(col.names = c("Terms", "β", "SE", "Z", "IC"), align = c("l", "c", "c", "c", "c"), escape = FALSE) %>% -->
<!--   add_header_above(c("HA (n nests = 2774)" = 5)) %>% -->
<!--   kable_classic(full_width = F, html_font = "Cambria") %>% -->
<!--   save_kable("ClimHA_Plast_Fixresults.png", zoom = 10) -->

<!-- read.csv("Climwin_HA_Plasticity.csv") %>% -->
<!--   mutate(across(where(is.numeric), ~round(., digits = 2))) %>% -->
<!--   kbl(col.names = c("Random effects", "σ²", "σ"), -->
<!--                                align = c("l", "c", "c")) %>% -->
<!--   kable_classic(full_width = F, html_font = "Cambria") %>% -->
<!--   save_kable("ClimHA_Plast_Ranresults.png", zoom = 10) -->

<!-- ``` -->


# Create sample table
```{r}
Sample_size <- data.frame("SampleSize_nests" = c(SampleSize_nests),
                          "SampleSize_females" = c(SampleSize_females),
                          "Sample_size_plast_fem" = c(Sample_size_plast_fem),
                          "Sample_size_plast_nest" = c(Sample_size_plast_nest))
write_csv(Sample_size, "Sample_size.csv")
```








<!-- # Performing analysis Males -->

<!-- ```{r} -->
<!-- Data <- read.csv("RefittedDATAHASize.csv", header = T, sep = ",", -->
<!--                  stringsAsFactors = F) -->
<!-- Data_HA <- Data %>% -->
<!--   filter(CONFIRMMACH == "t") %>% -->
<!--   filter(!ANILLOMACH == "SA") %>% -->
<!--   select(NIDO, WORKYEAR, HA, -->
<!--          ANILLOMACH, RealFatherAge, -->
<!--          RefittedSST, -->
<!--          RefittedArea_Rain, -->
<!--          PROPORTIONALRANK -->
<!--          ) %>% -->
<!--   mutate(across(c(WORKYEAR), as.character)) %>% -->
<!--   mutate(across(c(where(is.numeric), -HA), arm::rescale)) %>% -->
<!--   mutate(across(c(where(is.character)), as.factor)) %>% -->
<!--   drop_na() %>% -->
<!--   glimpse() -->

<!-- SampleSize_nests <- Data_HA %>% count() %>% pull() -->
<!-- SampleSize_males <- Data_HA %>% count(ANILLOMACH) %>% count() %>% pull() -->
<!-- Data_HA %>% count(ANILLOMACH) %>% filter(n>1) -->
<!-- SampleSize_males -->
<!-- Data_HA %>% ggplot(aes(HA)) + geom_bar() -->
<!-- ``` -->
<!-- ## Clmm model -->
<!-- ```{r} -->
<!-- ModClmm = clmm(factor(HA) ~ -->
<!--                  PROPORTIONALRANK + -->
<!--                  RefittedSST +  -->
<!--                  RefittedArea_Rain + I(RefittedArea_Rain^2) + -->
<!--                  RealFatherAge + I(RealFatherAge^2) + -->
<!--                  (1|WORKYEAR) + (1|ANILLOMACH), -->
<!--                data = Data_HA) -->

<!-- summary <- summary(ModClmm); summary -->

<!-- ``` -->
<!-- exp(-1.00038) = 0.367, which means that at each increase in SST female have a (1 - 0.367) = 63% lower odds of being less likely to apply lay a larger clutch size. -->

<!-- In other words likelihood of a clutch of 2 versus a clutch of 1 on the rating scale is multiplied by 0.3677 -->

<!-- ### Create FINAL clmm table -->
<!-- ```{r eval=FALSE} -->
<!-- # Table to results coef -->
<!-- FixCoef <- broom::tidy(ModClmm) -->
<!-- RanCoef <- data.frame(Term = c("Year", "Male ID"), -->
<!--                       Std.Dev. = c(summary$ST[[1]], -->
<!--                                    summary$ST[[2]])) %>% -->
<!--   mutate(Variance = Std.Dev.^2) -->

<!-- CI <- confint(ModClmm, level = 0.95) -->

<!-- CoefCLMMTable <- FixCoef %>% bind_cols(as.data.frame(CI)) -->

<!-- write_csv(CoefCLMMTable, "Climwin_CLMM_fixcoef.csv") -->
<!-- write_csv(RanCoef, "Climwin_CLMM_rancoef.csv") -->

<!-- Terms = c("Laying date","SST", "Rain", "Rain²", "Male age","Male age²") -->

<!-- read.csv("Climwin_CLMM_fixcoef.csv") %>% -->
<!--   select(-p.value, -coef.type) %>% mutate(across(where(is.numeric), ~round(., digits = 2))) %>% -->
<!--   unite("IC", `X2.5..`:`X97.5..`, sep = " | ") %>% dplyr::slice(-(1:2)) %>% -->
<!--   relocate(IC, .after = statistic) %>% -->
<!--   mutate(term = Terms) %>% kbl(col.names = c("Terms", "β", "SE", "Z", "IC"), align = c("l", "c", "c", "c", "c")) %>% -->
<!--   add_header_above(c("Clutch size (n nests = 3435)" = 5)) %>% -->
<!--   kable_classic(full_width = F, html_font = "Cambria") %>% -->
<!--   save_kable("ClimHA_Fixresults_male.png", zoom = 10) -->

<!-- read.csv("Climwin_CLMM_rancoef.csv") %>% -->
<!--   mutate(across(where(is.numeric), ~round(., digits = 2))) %>% -->
<!--   kbl(col.names = c("Random effects", "σ²", "σ"), -->
<!--                                align = c("l", "c", "c")) %>% -->
<!--   kable_classic(full_width = F, html_font = "Cambria") %>% -->
<!--   save_kable("ClimHA_Ranresults_Male.png", zoom = 10) -->

<!-- ``` -->




<!-- # Plasticity -->


<!-- ### Re-Import final data -->
<!-- ```{r} -->
<!-- Data <- read.csv("RefittedDATAHASize.csv", header = T, sep = ",", -->
<!--                  stringsAsFactors = F) -->
<!-- ``` -->

<!-- ### Add plasticity variables -->
<!-- We added to previous models the mean rainfall experienced across all nesting attempts (̄x rainfall ,a single term per individual female), as well as the deviation from the female‐specific mean rainfall for each of her separate nesting attempts (Δ rainfall, a single term per individual nest attempt) to examined their independent effects on success of each reproductive output. -->
<!-- ```{r} -->
<!-- Data_HA <- Data %>% -->
<!--   filter(CONFIRMMACH == "t") %>% -->
<!--   filter(!ANILLOMACH == "SA") %>% -->
<!--   select(NIDO, WORKYEAR, HA, -->
<!--          ANILLOMACH,  -->
<!--          RealFatherAge, -->
<!--          RefittedArea_Rain, RefittedSST,  -->
<!--          PROPORTIONALRANK) %>% -->
<!--   mutate(across(c(WORKYEAR), as.character)) %>% -->
<!--   mutate(across(where(is.character), as.factor)) %>% -->
<!--   drop_na() %>% -->
<!--   group_by(ANILLOMACH) %>% arrange(ANILLOMACH) %>% -->
<!--   mutate( -->
<!--     meanSST = mean(RefittedSST), -->
<!--     deltaSST = (RefittedSST - meanSST) -->
<!--   ) %>% -->
<!--   mutate(n = n()) %>% -->
<!--   ungroup() %>% -->
<!--   rowwise() %>% -->
<!--   mutate(bB_bW_SST = meanSST - deltaSST) %>% -->
<!--   ungroup() %>% -->
<!--   mutate(across(c(where(is.numeric), -HA, -contains("delta"), -n), arm::rescale)) %>% -->
<!--   filter(n > 1) %>% # Only use birds with multiple reads. This can cause that results may vary respect to previous analysis -->
<!--   glimpse() -->

<!-- Sample_size_plast_male <- Data_HA %>% count(ANILLOMACH) %>% count() %>% pull # half of females reproduced at least 2 or more times -->
<!-- Sample_size_plast_nest_males <- Data_HA %>% count() %>% pull # half of females reproduced at least 2 or more times -->

<!-- Sample_size_plast_male -->
<!-- Sample_size_plast_nest_males -->
<!-- ``` -->

<!-- ## Analysis of plasticity -->


<!-- ## Clmm model -->
<!-- ```{r} -->
<!-- ModClmm = clmm(factor(HA) ~ -->
<!--                  PROPORTIONALRANK + -->
<!--                  RefittedArea_Rain + I(RefittedArea_Rain^2) + -->
<!--                  meanSST + deltaSST + -->
<!--                  RealFatherAge + I(RealFatherAge^2) + -->
<!--                  (1|WORKYEAR) + (1|ANILLOMACH), data = Data_HA) -->

<!-- summary <- summary(ModClmm); summary -->

<!-- check_collinearity(ModClmm) -->
<!-- ``` -->


## Poisson distribution
```{r, eval=FALSE, echo=FALSE}
# Poisson distribution
var(Data_HA$HA) #  mean /= variance we don't need to use quasi poisson
mean(Data_HA$HA)

ModGlmm = glmmTMB(HA ~                 
                 meanSST + deltaSST +
                 PROPORTIONALRANK +
                 RefittedArea_Rain + #I(RefittedArea_Rain^2) +
                 AGEHEMB +
                 (1|WORKYEAR) + (1|ANILLOHEMB),
                  family = poisson,
                  ziformula = ~0,
                  REML = F,
                  data = Data_HA)

summary(ModGlmm)
check_collinearity(ModGlmm)
```

# Plot
```{r, eval=FALSE, echo=FALSE}
plot(allEffects(ModGlmm))
```


```{r, eval=FALSE, echo=FALSE}
ModGlmm = glmmTMB(HA ~                 
                 bB_bW_SST + deltaSST +
                 PROPORTIONALRANK +
                 RefittedArea_Rain + #I(RefittedArea_Rain^2) +
                 AGEHEMB +
                 (1|WORKYEAR) + (1|ANILLOHEMB),
                  family = poisson,
                  ziformula = ~0,
                  REML = F,
                  data = Data_HA)
summary(ModGlmm)
```